Catchy Title Goes Here

### 2018-06-20 Paper/paper.tex
updated results text for Figure 3

The left panel of Fig.~\ref{fig:sero} the color-coded provinces. We use these colors throughout this section to show the results from individual provinces. The right panel shows the recovered seroprevalence data (right panel) for all 11 provinces, using all three datasets (solid line) and the vaccination and case data only (dashed lines). The solid line is the mean of the posterior distribution generated using all three datasets, while the dashed lines show the full range of the posterior for the vaccination/case data analysis. We see that, in general, the seroprevalence data leads to a \emph{lower} estimate of seroprevalence in the population than the case and vaccination data alone. This is because the prior on vaccine effectiveness is peaked around $0.85$ - that is, when a study participant reports that they or their child is vaccinated, we give an $85\%$ probability that not only is the recollection correct, but that the vaccine produced immunity. Without seroprevalence data, there is not enough information in the datasets to pull the value for $\gamma$ away from this peak, and so we overestimate the immunity in the population. This is particularly noticeable in the results for Sud Kivu. The only province for which this is not the case is Maniema, but looking at the seroprevalence data for Maniema reveals many age groups for which $100\%$ of the population are seropositive. This suggests either a small number of participants, which could be taken into account in future analyses, or something that went wrong with the data reporting.

@@

In the next figure, Fig.~\ref{fig:foivaccveff}, we examine the vaccination hazard and probability, the force of infection, and the vaccine efficacy for each of the eleven provinces, inferred using all three datasets. The left panel shows the vaccination data as points, the vaccination hazard as solid lines, and the vaccination probability as dashed lines. All curves are generated from samples drawn from the posterior distributions of the model parameters. For almost all of the provinces, the vaccination hazard is peaked tightly around approximately one year in age, as expected. The height of the vacc. hazard corresponds closely to the final level of vaccination probability - higher vaccination hazard means a higher probability of getting vaccinated. The only province that does not follow this pattern is Bas Congo, for which there is evidence for a vaccination hazard with non-negligible weight at higher ages. That is, the probability of being vaccinated is still increasing at the right edge of this graph, which corresponds to five years old.

The next (middle) panel in Fig.~\ref{fig:foivaccveff} shows the force of infection recovered for each province using all data (solid) and vaccionation/case data (dashed). For all provinces except Equateur, the force of infection is either Weibull plus constant (first seven cells), or constant-only (final four cells) for both datasets. In Equateur, the simpler model is used when vaccination/case data only are used. We see here that all provinces have a non-zero force of infection at higher ages.

The final (right) panel in Fig.~\ref{fig:foivaccveff} shows the mean value and uncertainty for vaccine efficacy ($\bar{\gamma} \pm \sigma$) for all eleven provinces, with the same color-coding as has been used throughout this section. As expected from the serology results, Sud Kivu has the lowest vaccine efficacy. Because of our results using the simulated data, we believe that the ordering of provinces by $\gamma$ is correct - but we do not believe that the actual values should be taken seriously. From that analysis, we suspect that the recovered values are likely lower than the true values.

>>>>

%The left panel of Fig.~\ref{fig:sero} the color-coded provinces. We use these colors throughout this section to show the results from individual provinces. The right panel shows the recovered seroprevalence data (right panel) for all 11 provinces, using all three datasets (solid line) and the vaccination and case data only (dashed lines). The solid line is the mean of the posterior distribution generated using all three datasets, while the dashed lines show the full range of the posterior for the vaccination/case data analysis. We see that, in general, the seroprevalence data leads to a \emph{lower} estimate of seroprevalence in the population than the case and vaccination data alone. This is because the prior on vaccine effectiveness is peaked around $0.85$ - that is, when a study participant reports that they or their child is vaccinated, we give an $85\%$ probability that not only is the recollection correct, but that the vaccine produced immunity. Without seroprevalence data, there is not enough information in the datasets to pull the value for $\gamma$ away from this peak, and so we overestimate the immunity in the population. This is particularly noticeable in the results for Sud Kivu. The only province for which this is not the case is Maniema, but looking at the seroprevalence data for Maniema reveals many age groups for which $100\%$ of the population are seropositive. This suggests either a small number of participants, which could be taken into account in future analyses, or something that went wrong with the data reporting.

@@

The resulting age-specific hazards for vaccination and FOI illustrate significant province-level variation.  Vaccination at the province-level exhibits strong differences in both the maximum coverage achieved and the timeliness (e.g. the variance of the vaccine hazard) (FIG REF a).  The hazard of vaccination falls to near 0 by approximately 24 months of age in all provinces except for Bas Congo, where the proportion of children vaccinated continues to increase over the full age range (6-59 months) included in the DHS survey (FIG REF a). In the 7 provinces for which the Weibull plus constant FOI hazard was selected, the mode of the fitted FOI was at or below 5 years of age (FIG REF b).  In 6 of 7 of these provinces, the FOI hazard rate dropped to near 0 by 10 years of age, suggesting little additional infection risk beyond 10 years of age.  In all 7 of these provinces, the fitted hazard rate for the model with and without serology data included were similar.  Equateur province stands out as an exception, here the FOI was highest of all provinces and remained high through adolescence. Notably, the mean age of infection among reported cases was highest in Equateur province. In the 4 provinces for which the contant hazard rate model was the best fit the rates were similar for models fit with and without the inclusion of serology data (FIG REF b).

There was high variability in the estimated vaccine effectiveness in the 11 provinces.  In 8 of 11 provinces, the fitted values are considerably lower than the conventionally assumed vaccine effciacy of ~85\% for measles vaccine [REF Uzacanin paper]. Based on the results from the simulation study, above, the absolute value of these estimates should be taken with caution; however, they may reflect a qualitative ranking of effectiveness, or the reliabilty of vaccination survey responses in these provinces.  The 4 provinces with the lowest values, Bandundu, Sud Kivu, Kasia Occidental, and Kasai Oriental, all reported relatively high vaccination coverage in the 2014 DHS relative to the seroprevalence.  Thus, low effectiveness is consistent with this observation.  Notably, this is corroborated by low estimated effectiveness when the model is fit in the absence of serological data.

%In the next figure, Fig.~\ref{fig:foivaccveff}, we examine the vaccination hazard and probability, the force of infection, and the vaccine efficacy for each of the eleven provinces, inferred using all three datasets. The left panel shows the vaccination data as points, the vaccination hazard as solid lines, and the vaccination probability as dashed lines. All curves are generated from samples drawn from the posterior distributions of the model parameters. For almost all of the provinces, the vaccination hazard is peaked tightly around approximately one year in age, as expected. The height of the vacc. hazard corresponds closely to the final level of vaccination probability - higher vaccination hazard means a higher probability of getting vaccinated. The only province that does not follow this pattern is Bas Congo, for which there is evidence for a vaccination hazard with non-negligible weight at higher ages. That is, the probability of being vaccinated is still increasing at the right edge of this graph, which corresponds to five years old.

%The next (middle) panel in Fig.~\ref{fig:foivaccveff} shows the force of infection recovered for each province using all data (solid) and vaccionation/case data (dashed). For all provinces except Equateur, the force of infection is either Weibull plus constant (first seven cells), or constant-only (final four cells) for both datasets. In Equateur, the simpler model is used when vaccination/case data only are used. We see here that all provinces have a non-zero force of infection at higher ages.

%The final (right) panel in Fig.~\ref{fig:foivaccveff} shows the mean value and uncertainty for vaccine efficacy ($\bar{\gamma} \pm \sigma$) for all eleven provinces, with the same color-coding as has been used throughout this section. As expected from the serology results, Sud Kivu has the lowest vaccine efficacy. Because of our results using the simulated data, we believe that the ordering of provinces by $\gamma$ is correct - but we do not believe that the actual values should be taken seriously. From that analysis, we suspect that the recovered values are likely lower than the true values.
